## Vectors, Lists, and Data frames

### Numeric vectors

R operates on _data structures_. The simplest data structure is a _numeric vector_, defined as an ordered collection of numbers. A single number is a vector of length 1, for example, in the code below, a vector with a single number, `3`, is assigned to `x`.

```{r}
x <- 3
```

A vector with multiple numeric components can be created using the `c()` function, which _concatenates_ each element. For example, a vector consisting of three numbers, `9`, `2`, and `8` can be assigned to `x` with the following code.

```{r}
x <- c(9, 2, 8)
```


#### Exercise

Create a vector with 4 elements: `2`, `4`, `6`, `8`

```{r vector, exercise = TRUE}

```

```{r vector-check}
grade_result(
 pass_if(~ identical(.result, c(2,4,6,8)))
)
```

### Vector arithmetic

Arithmetic can be performed on vectors; the expressions will be applied element by element. For example, two vectors can be added using the `+`, as seen below.

```{r}
c(1, 2, 3) + c(3, 2, 1)
```

If the vectors are not of the same length, the elements of the shorter vector(s) will be _recycled_ to complete the expression.

```{r}
c(1, 2) + c(1, 2, 3, 4)
```

For example, above the vector `c(1, 2)` was repeated so that it has length `4`, resulting in `c(1, 2, 1, 2)` to match the length of `c(1, 2, 3, 4)`.

Additional common arithmetic functions include:

* `log()`
* `exp()`
* `sqrt()`
* `min()`
* `max()`
* `mean()`
* `var()`

#### Exercises

Edit the code below to multiply vector `x` by vector `y`.

```{r vector-mult, exercise = TRUE}
x <- c(1, 8, 6, 7)
y <- c(5, 3, 0, 9)
```

```{r vector-mult-check}
x <- c(1, 8, 6, 7)
y <- c(5, 3, 0, 9)
grade_result(
  pass_if(~ identical(.result, x * y))
)
```

Take the `log()` of the vector `x` below and multiply this result by `10`.

```{r vector-log, exercise = TRUE}
x <- c(1, 8, 6, 7)
```

```{r vector-log-check}
x <- c(1, 8, 6, 7)
grade_result(
  pass_if(~ identical(.result, log(x) * 10))
)
```

### Logical vectors

In addition to numeric vectors, `R` also allows for _logical_ vectors. These vectors can consist of the values: `TRUE`, `FALSE`, and `NA` (meaning "not available" indicating a missing value). These vectors are generated by conditions, created with the following logicial operators:

* `<`: less than
* `<=`: less than or equal to
* `>`: greater than
* `>=`: greater than or equal to
* `==`: equal 
* `!=`: not equal
* `&`: logical AND (element wise comparison)
* `&&`: logical AND (evaluates left to right, examining only the first element of each vector)
* `|`: logical OR (element wise comparison)
* `||`: logical OR (evalutes left to right, examining only the first element of each vector)
* `!`: logical negtation (NOT)

For example, the following code creates a logical vector assessing whether each element of the vector `x` is greater than `4`

```{r}
x <- c(8, 6, 7, 5, 3, 0, 9)
x > 4
```

#### Exercises

Check whether each element of `x` is greater than or equal to `3`.

```{r logical, exercise = TRUE}
x <- c(8, 6, 7, 5, 3, 0, 9)
```

```{r logical-check}
x <- c(8, 6, 7, 5, 3, 0, 9)

grade_result(
  pass_if(~ identical(.result, x >= 3))
)
```

Check whether each element of `x` is greater than 5 AND less than or equal to 7.

```{r logical-2, exercise = TRUE}
x <- c(8, 6, 7, 5, 3, 0, 9)
```

```{r logical-2-check}
x <- c(8, 6, 7, 5, 3, 0, 9)

grade_result(
  pass_if(~ identical(.result, x > 5 & x <= 7))
)
```

### Character vectors

It is also possible to store _character_ values in a vector. Character strings are entered in `R` using quotation marks, either `'` or `"`, for example below is a character vector with the first three letters in the alphabet.

```{r}
c("a", "b", "c")
```

#### Exercise

Create a character vector with the values: "apple" "banana" and "pear"

```{r vector-char, exercise = TRUE}

```

```{r vector-char-check}
grade_result(
  pass_if(~ identical(.result, c("apple", "banana", "pear")))
)
```

### Indexing vectors

You can _index_ a vector by using a square bracket, `[]` with the desired index vector. There are four types of index vectors

1. A logical vector
2. A vector of positive integers
3. A vector of negative integers
4. A character vector

#### Logicial vectors

Using a logical vector, `x`, to index another vector, `y`, will select only the values of `y` for which the conditions for `x` are `TRUE`. For example, if `x` is `c(TRUE, FALSE, TRUE)`, the first and third element of `y` will be selected. It works like this. The `x` vector, or the logical index vector, will be placed in a square bracket appended to the vector `y`.

```{r}
y <- c(1, 2, 3)
y[c(TRUE, FALSE, TRUE)]
```

#### Vectors of positive integers

Using a vector of positive integers, `x`, to index another vector, `y`, will select only the values of `y` that correspond to the position dictated by `x`. For example, if `x` is `c(1, 2)`, the first and second element of `y` will be selected.

```{r}
y <- c(3, 4, 5)
y[c(1, 2)]
```

#### Vectors of negative integers

Using a vector of negative integers, `x`, to index another vector, `y`, will select only the values of `y` that correspond to the position NOT in `x`. For example, if `x` is `-c(1, 2)`, the first and second element of `y` will NOT be selected.

```{r}
y <- c(3, 4, 5)
y[-c(1, 2)]
```

#### Vectors of character strings

If a vector has a _names_ attribute, the elements can be selected using a character vector. 

```{r}
fruits <- c(1, 2, 3)
names(fruits) <- c("apple", "banana", "pear")
fruits[c("pear", "apple")]
```


#### Exercise

Select the second, fourth, and fifth elements of the vector, `x`, below.

```{r index, exercise = TRUE}
x <- 1:10
```

```{r index-check}
x <- 1:10
grade_result(
  pass_if(~ identical(.result, x[c(2, 4, 5)]))
)
```


Create a vector `y` containing the values that are greater than 2 in vector `x`. 

```{r index2, exercise = TRUE}
x <- c(1:10)
```


```{r index2-check}
grade_result(
  pass_if(~identical(.result, y <- x[x>2] ))
)
```


### Lists

An `R` _list_ is data structure consisting of an ordered collection of _components_. The components can be of different modes and types, for example, a list could be a collection of different types of vectors of different lengths, as seen below.

```{r}
list(numeric = c(1, 2, 3), 
     logical = TRUE,
     character = c("apple", "banana"))
```

Components of the list are _numbered_ and can be referenced using a double bracket. For example, you can reference the first element of a list with `[[1]]` as seen below.

```{r}
lst <- list(numeric = c(1, 2, 3), 
     logical = TRUE,
     character = c("apple", "banana"))
lst[[1]]
```

Components can also be referenced via their _names_. For example, the first element of the list below could be referenced by `[["numeric"]]`

```{r}
lst[["numeric"]]
```

#### Exercise

Combine the following four vectors into a list.

```{r list, exercise = TRUE}
x <- c(5, 1, 3)
y <- 1
z <- c("chickens", "roosters")
```

```{r list-check}
x <- c(5, 1, 3)
y <- 1
z <- c("chickens", "roosters")
grade_result(
  pass_if(~ identical(.result, list(x, y, z)))
)
```

### Data frames

A _data frame_ is a specific type of _list_ with the class `data.frame` or `tibble`. A `tibble` is a specific subclass of `data.frame` that has a few additional restrictions. Broadly, data frames consist of _rows_ and _columns_, where the length of the _rows_ is consistent for all _columns_. For example, here is a data frame with two columns, `x` and `y`, each with three rows.

```{r}
data.frame(
  x = c(1, 2, 3),
  y = c(4, 5, 6)
)
```

#### Exercise

Create a data frame using the `data.frame()` function consisting of two variables, `x` and `y`, detailed below.

```{r dataframe, exercise = TRUE}
x <- c(1, 2, 3)
y <- c("do", "re", "mi")
```

```{r dataframe-check}
x <- c(1, 2, 3)
y <- c("do", "re", "mi")
grade_result(
  pass_if(~ identical(.result, data.frame(x = x, y = y)))
)
```




