## Manipulating data

You can manipulate data frames. In this lesson, we will learn how to:

* Filter or _subset_ a data frame's rows based on particular conditions
* Select or _subset_ a data frame's columns 
* Add variables to a data frame
* Summarize columns in a data frame


### Filtering or subsetting rows

To filter rows of a data frame, you can use the `subset()` function with the `subset` argument. For example, here is a data frame included in `R` called `mtcars`. This data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
mtcars
```

If you wanted to filter this data frame to only include rows of cars that have miles per gallon (`mpg`) greater than 25, you would do the following:

```{r}
subset(mtcars, subset = mpg > 25)
```

You can save this new filtered data frame by assigning it to a new object using the `<-`:

```{r}
mtcars_subset <- subset(mtcars, subset = mpg > 25)
```

If you want to subset based on more than one condition, you can use **logical operators** discussed in a previous section. For example, if you want to filter to only include rows where `mpg` is greater than 25 and weight (`wt`) is greater than 2, you would do the following:

```{r}
subset(mtcars, subset = mpg > 25 & wt > 2)
```

#### Exercise

Filter the `mtcars` data frame to only include rows where the gross horsepower (`hp`) is less than 100.

```{r filter, exercise = TRUE}
mtcars
```

```{r filter-check}
grade_result(
  pass_if(~ identical(.result, subset(mtcars, hp < 100)))
)
```

```{r filter-solution}
subset(mtcars, hp < 100)
```


### Selecting or subsetting columns

To select specific columns, you can also use the `subset()` function. Instead of specifying the `subset` argument (that would filter the rows), you can specify the `select` argument to select specific columns. For example, if you want to create a data frame that only includes the `mpg` column, you can do the following:

```{r}
subset(mtcars, select = mpg)
```

If you would like to only include both `mpg` and `cyl`, you can pass a **vector**, `c(mpg, cyl)` to the `select` argument.

```{r}
subset(mtcars, select = c(mpg, cyl))
```

If you would like to include **all** columns _except_ `mpg`, you can use the `-` sign as shown below.

```{r}
subset(mtcars, select = - mpg)
```

#### Exercises

Create a new data frame called `mtcars_disp` that only includes the `disp` column from the `mtcars` data frame.

```{r select, exercise = TRUE}

```

```{r select-check, warning = FALSE}
mtcars_disp <- subset(mtcars, select = disp)
grade_result(
  pass_if(~ identical(.result, mtcars_disp))
)
```

```{r select-solution}
mtcars_disp <- subset(mtcars, select = disp)
```

Create a new data frame called `mtcars_new` that _filters_ rows to only include rows where `wt` is less than 2 and _selects_ two columns, `wt` and `mpg`.

```{r select-2, exercise = TRUE}

```

```{r select-2-check, warning = FALSE}
mtcars_new <- subset(mtcars, subset = wt < 2, select = c(wt, mpg))
grade_result(
  pass_if(~ identical(.result, mtcars_new))
)
```

```{r select-2-solution}
mtcars_new <- subset(mtcars, subset = wt < 2, select = c(wt, mpg))
```


### Add variables to a data frame

There are many ways to add a column to a data frame. Two are the following:

* via the `$`
* via the `cbind()` function

A variable can be referenced in a data frame using the `$`. For example, using the `mtcars` data frame, you can reference the `mpg` column using `mtcars$mpg`. You can add a _new_ variable by assigning a vector to the new variable, as below:

```{r}
mtcars$new_var <- 1:32
```

Alternatively, a new variable can be added using the `cbind()` function. In order to ensure that this new variable is _saved_, you must assign the new data frame created with `cbind()`

```{r}
new_var <- 1:32

mtcars <- cbind(mtcars, new_var)
```

#### Exercise

Below is a data frame called `df` with one variable, `x`. Add a variable called `y` that is equal to `c(1, 2, 3)`. Then output `df`.

```{r add-var, exercise = TRUE}
df <- data.frame(x = c("a", "b", "c"))
## Add a variable called y
df
```

```{r add-var-check}
grade_result(
  pass_if(~ identical(.result, data.frame(x = c("a", "b", "c"),
                                          y = c(1, 2, 3))))
)
```

```{r add-var-solution}
df <- data.frame(x = c("a", "b", "c"))
df$y <- c(1, 2, 3)
df
```

### Summarise columns in a data frame

In `R`, you can use functions to summarise observations in a column of a data frame. For example, to take the average, or mean, of a column, you can use the `mean()` function and reference the data frame's column using the `$`. To take the average of the miles per gallon (`mpg`) column in the `mtcars` data frame, you would run the following:

```{r}
mean(mtcars$mpg)
```

If you want to summarise observations in a column by another column, one way to do this is using the `aggregate()` function. For example, if you wanted to calculate the average miles per gallon (`mpg`) by the number of cylinders (`cyl`) using the `mtcars` data, you would run the following:

```{r}
aggregate(mpg ~ cyl, data = mtcars, FUN = mean)
```

If instead of taking the average, you wanted to take sum the miles per gallon (`mpg`) by the number of cylinders (`cyl`), you would change the `FUN` argument to `sum` as below:

```{r}
aggregate(mpg ~ cyl, data = mtcars, FUN = sum)
```

#### Exercise

Using the `mtcars` data, calculate the average weight (`wt`) by the transmission (`am`). 

```{r avg, exercise = TRUE}

```

```{r avg-check}
grade_result(
  pass_if(~ identical(.result, aggregate(wt ~ am, data = mtcars, FUN = mean)))
)
```

```{r avg-solution}
aggregate(wt ~ am, data = mtcars, FUN = mean)
```


