## Manipulating tidy data

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(nycflights13)
```

<!-- Adapted from Hannah's tutorial: https://github.com/hluebbering/tidyverse-manipulating-data/ -->

In this section, we’re focusing on how to use a core tidyverse package to manipulate data: **the dplyr package.**

To explore **dplyr**’s basic data manipulation methods, we will learn how to use the following functions:

* Subset or `filter()` a data frame’s observations by picking their values 
* Pick variables or `select()` a data frame’s columns
* Add or `mutate()` variables to a data frame
* Condense or `summarize()` variables down to a single summary 

### Filtering or subsetting rows

To filter rows of a data frame, you can use the `filter()` function. As an example, we will manipulate the `flight` data frame from the **nycflights13** package. 

This data frame includes 336,776 flights that departed from New York City in 2013. The data comes from the US Bureau of Transportation Statistics.

```{r table1}
flights
```

If you wanted to **filter** this data frame to only include rows of flights that only went out on January 1st, you would do the following:

```{r filt, eval = FALSE}
filter(flights, month == 1, day == 1)
```

Notice the first argument is the original data frame, `flights`, and the subsequent arguments are the logical predicates defined in terms of the variables in the original data frame. The first argument for all functions used to manipulate data in the **tidyverse** is the data frame you are manipulating. When you run the above line of code, **dplyr** executes the filtering operation and returns a new data frame. 

```{r table2}
filter(flights, month == 1, day == 1)
```


**dplyr** functions never alter their inputs. If you want to save the results, you must use the assignment operator `<-`

```{r save}
jan1 <- filter(flights, month == 1, day == 1)
```

If you want to filter the data frame based on more than one condition, you can use **logical operators**. 

For example, if you want to only include rows of flights that weren’t delayed (on arrival or departure) by more than two hours, you would do the following:

```{r log}
filter(flights, arr_delay <= 120, dep_delay <= 120)
```


#### Exercise

Modify the code below to **filter** the `flights` data frame to only include rows of flights that went out on December 25th:

```{r grade_filter, exercise = TRUE}
filter(flights, month == 1, day == 1)
```

```{r grade_filter-check}
grade_result(
  pass_if(~ identical(.result, filter(flights, month == 12, day == 25)))
)
```

```{r grade_filter-solution}
filter(flights, month == 12, day == 25)
```

### Selecting or subsetting columns

To **select** specific columns, you can use the `select()` function. For example, if you want to create a data frame that only includes the `year` column, you can do the following:


```{r select-ex}
select(flights, year)
```


Notice again that the first argument of the `select()` function is the data frame that is being manipulated, in this case `flights`. The subsequent arguments are the variables that you would like to select. If you would like to only include `year`, `month`, and `day` you can do the following:

```{r select2}
select(flights, year, month, day)
```

Alternatively, you can use expressions like `x:y` to select ranges of variables. For example, since the columns `year`, `month`, `day` in the `flights` data frame are in that order, we can select them as follows:

```{r select3}
select(flights, year:day)
```

If you would like to include **all** columns _except_ `year`, `month`, and `day` you can use the `-` sign as shown below:

```{r select-flights-day}
select(flights, -(year:day))
```


#### Exercises

Create a new data frame called `flights_month` that only includes the `month` column from the `flights` data frame.

```{r grade_select, exercise = TRUE}

```

```{r grade_select-check}
grade_result(
  pass_if(~ identical(.result, select(flights, month)))
)
```

```{r grade_select-solution}
select(flights, month)
```



Filter the `flights` data frame to only include rows where `arr_delay` is less than or equal to 120 minutes and select the following columns: `dep_time`, `sched_dep_time`.

```{r grade_select2, exercise = TRUE}

```

```{r grade_select2-check}
grade_result(
  pass_if(~ identical(.result, 
                      select(filter(flights, arr_delay <= 120),
                             dep_time, sched_dep_time)))
)
```

```{r grade_select2-solution}
select(filter(flights, arr_delay <= 120),
       dep_time, sched_dep_time)
```


### Add variables to a data frame

We can **add new columns** that are transformations of existing columns with the `mutate()` function. The `mutate()` function always adds new columns to the end of the data set. 

For example, we can add two columns to the `flights` data frame using the `mutate()` function as follows:

```{r mutate2}
mutate(flights,
       gain = dep_delay - arr_delay,
       speed = distance / air_time * 60
)
```

Notice again that the first argument is the data frame being manipulated and the subsequent arguments are name-value pairs of expressions with the name indicating the name of the new variable being created and the value it's corresponding value.

If you only want to keep the new variables, use `transmute()`:

```{r transmute}
transmute(flights,
          gain = dep_delay - arr_delay,
          hours = air_time / 60,
          gain_per_hour = gain / hours
)
```


#### Exercise

Using the `flights` data, add a variable `speed` that is equal to `distance / air_time * 60`:


```{r grade_mutate, exercise = TRUE}

```


```{r grade_mutate-check}
grade_result(
  pass_if(~ identical(.result, 
                      mutate(flights, speed = distance / air_time * 60)))
)
```


```{r grade_mutate-solution}
mutate(flights,
       speed = distance / air_time * 60
)
```

### Summarize columns in a data frame

With **dplyr**, you can use functions to summarize observations in a column of a data frame using the `summarize()` function and the `group_by()` function.

For example, we can calculate the average delay per date by running the following:

```{r summary}
by_day <- group_by(flights, year, month, day)
summarize(by_day, delay = mean(dep_delay, na.rm = TRUE))
```

Notice that the first argument of both `group_by()` and `summarize()` is the data frame being grouped and summarized, respectively. _Note, when using aggregation functions, we have an `na.rm = TRUE` argument that removes missing values before computation._

#### Exercise

Calculate the average amount of time spent in the air, `air_time` by `year` in the `flights` data frame. Group the `flight` data by `year` and then summarize the `mean` `air_time`.

```{r grade_summarize, exercise = TRUE, eval = FALSE}
by_year <- group_by(---, ---)
summarize(by_year, mean(----, na.rm = TRUE))
```

```{r grade_summarize-solution}
by_year <- group_by(flights, year)
summarize(by_year, mean(air_time, na.rm = TRUE))
```

```{r grade_summarize-check}
by_year <- group_by(flights, year)
grade_result(
  pass_if(~ identical(.result, 
                      summarize(by_year, mean(air_time, na.rm = TRUE))))
)
```

### Pipes

Rather than giving each data frame a name, we can use the pipe: `%>%`.

- The pipe improves the readability of code since you can read the code from left-to-right
- We can read it as a series of commands for example: group, then summarize, then filter

For example here's a summary of the flights average departure delay, `dep_delay`, grouped by `year`, `month`, and `day`:


```{r flights-summary}
flights %>% 
  group_by(year, month, day) %>% 
  summarize(mean = mean(dep_delay, na.rm = TRUE))
```

Suppose we want to remove the missing values prior to our calculation. We can solve this issue by removing all flights missing departure times from the data set then grouping, then summarising.

```{r cancel}
flights %>% 
  filter(!is.na(dep_delay)) %>%
  group_by(year, month, day) %>% 
  summarize(mean = mean(dep_delay))
```


#### Exercise

Using the `flights` data, find the the flights average `distance` grouped by `year`, `origin`, `dest`, and `arr_delay`. Call this new column `mean_distance`.

```{r flights_summary, exercise = TRUE}

```

```{r flights_summary-solution}
flights %>% 
  group_by(year, origin, dest, arr_delay) %>% 
  summarize(mean_distance = mean(distance, na.rm = TRUE))
```

```{r flights_summary-check}
grade_result(
  pass_if(~ identical(.result, flights %>% 
  group_by(year, origin, dest, arr_delay) %>% 
  summarize(mean_distance = mean(distance, na.rm = TRUE))))
)
```
