## Reading data

You can read data into R using `read.*()` functions. These include:

* `read.csv()`: Reads in `.csv` files by default
* `read.delim()`: Reads in tab-delimited files by default

The first argument of each of these functions is the `file`, the name of the file where the data are to be read from. 

For example, we have a file `sleep.csv` in a folder called `data` that contains data on the effect of two drugs on 10 patients' sleep.

```
"extra","group","ID"
 0.7,   "1",    "1"
-1.6,   "1",    "2"
-0.2,   "1",    "3"
-1.2,   "1",    "4"
-0.1,   "1",    "5"
.        .       . 
.        .       . 
.        .       . 
```

```{r}
read.csv(file = "data/sleep.csv")
```

We can save this data frame to an object in R using the assignment operator, `<-`

```{r}
sleep_data <- read.csv(file = "data/sleep.csv")
```

### Exercise

Read in the csv located at `data/airquality.csv` into R.


```{r, csv-setup}
tmp <- read.csv("https://raw.githubusercontent.com/wfu-dmds/teaching-r-study/master/learnr-module/data/airquality.csv")
fs::dir_create("data")
write.csv(tmp, "data/airquality.csv", row.names = FALSE)
tmp <- NULL
```

```{r csv, exercise = TRUE}

```

```{r csv-check}
grade_result(
  pass_if(~ identical(.result, read.csv("data/airquality.csv")))
)
```

```{r csv-solution}
read.csv("data/airquality.csv")
```






