## Tidy data frames

The [tidyverse](https://tidyverse.tidyverse.org/articles/paper.html) is a collection of R packages that help solve data science challenges. This collection of packages share the same design philosophy, grammar, and data structures. You can install the collection of tidyverse packages in R by running `install.packages("tidyverse")` in the console. To attach the packges within an R session, run the following:

```{r, eval = FALSE}
library(tidyverse)
```

Within the tidyverse paradigm, the main data structure of interest is the **tibble**. A **tibble** is a data frame with specific default behavior. 

Broadly, tibbles consist of _rows_ and _columns_, where the length of the _rows_ is consistent for all _columns_. For example, here is a tibble with two columns, `x` and `y`, each with three rows.

```{r}
tibble(
  x = c(1, 2, 3),
  y = c(4, 5, 6)
)
```


#### Exercise

Create a tibble using the `tibble()` function consisting of two variables, `x` and `y`, detailed below.

```{r tibble, exercise = TRUE}
x <- c(1, 2, 3)
y <- c("do", "re", "mi")
```

```{r tibble-check}
x <- c(1, 2, 3)
y <- c("do", "re", "mi")
grade_result(
  pass_if(~ identical(.result, tibble(x = x, y = y)))
)
```

### Variable classes

Each column in a tibble has a specific _class_. 

Common column classes include:

class | definition | example
------|------------|------
double (numeric) | double-precision floating point number | `1.5`
integer (numeric) | whole number | `1L`
logical | logical constant, either TRUE or FALSE  | `TRUE`
character | a character string | `"this is a string"`
list | an ordered collection of _components_ that can be of different modes and types | `list(1, "two", 3)`

Every element in the column must belong to the same class. For example, here is a tibble with

```{r}
tibble(
  numeric = 1:5,
  logical = TRUE,
  character = LETTERS[1:5]
)
```

Notice here the class of the column is printed below the variable name. The first column `numeric` is an integer, as indicated by `int`. The second column `logical` is logical, as indicated by `lgl`. The third column `character` is a character string, as indicated by `chr`. Also notice that even though `TRUE` was only entered once, it is repeated 5 times to match the length of the other columns. Tibbles will automatically recycle inputs of length 1.

```{r}
tibble(
  a = c(1, 2, 3),
  b = c("one", "two", "three"),
  c = list("one", 2, "three")
)
```

```{r tib-type1, echo = FALSE}
question("**In the tibble ablove, what is the class for variable `a`**",
  answer("double", correct = TRUE),
  answer("intever"),
  answer("logical"),
  answer("character"),
  answer("list")
)
```

```{r tib-type2, echo = FALSE}
question("**In the tibble ablove, what is the class for variable `b`**",
  answer("double"),
  answer("intever"),
  answer("logical"),
  answer("character", correct = TRUE),
  answer("list")
)
```

```{r tib-type3, echo = FALSE}
question("**In the tibble ablove, what is the class for variable `c`**",
  answer("double"),
  answer("intever"),
  answer("logical"),
  answer("character"),
  answer("list", correct = TRUE)
)
```

### Saving tibbles

You can save a tibble locally during an R session by _assigning_ it to a name using `<-`. For example, the code below assigns the tibble to `df`.


```{r}
df <- tibble(
  numeric = 1:5,
  logical = TRUE,
  character = LETTERS[1:5]
)
```

#### Exercise

Create a tibble from the two vectors below, `x` and `y`. Assign this tibble to `dat`.

```{r assign-tib, exercise = TRUE}
x <- c(8, 6, 7)
y <- c(5, 3, 0)

```

```{r assign-tib-solution}
dat <- tibble(
  x = c(8, 6, 7),
  y = c(5, 3, 0)
)
```


### Subsetting tibbles

You can _subset_ a tibble by using a single square bracket `[row(s), column(s)]`, indicating the rows and columns you'd like to keep by number, or using the double square bracket, `[[column]]` to extract a single column, indicated by name or by position. For example below, if I wanted to subset `df` to only contain rows 1 and 2 and column 3, I would use the single square bracket as follows.

```{r}
tibble(
  numeric = 1:5,
  logical = TRUE,
  character = LETTERS[1:5]
)
```

```{r}
df[c(1, 2), 3]
```

Alternatively, I could use the double square brackets to extract the `character` column and output just the values. The code below does this by _name_.

```{r}
df[["character"]]
```

Equivalently, I can do this by _position_, since `character` is the third column in the `df` tibble.

```{r}
df[[3]]
```

#### Exercise

Subset the tibble below to only contain the 1st and 3rd rows and the 2nd and 4th columns.

```{r subset-tibble, exercise = TRUE}
df <- tibble(
  a = 1:4,
  b = 5:8,
  c = c("a", "b", "c", "d"),
  d = c(TRUE, FALSE, TRUE, FALSE)
)

```

```{r subset-tibble-check}
df <- tibble(
  a = 1:4,
  b = 5:8,
  c = c("a", "b", "c", "d"),
  d = c(TRUE, FALSE, TRUE, FALSE)
)
grade_result(
  pass_if(~ identical(.result, df[c(1, 3), c(2, 4)]))
)
```

```{r subset-tibble-solution}
df <- tibble(
  a = 1:4,
  b = 5:8,
  c = c("a", "b", "c", "d"),
  d = c(TRUE, FALSE, TRUE, FALSE)
)
df[c(1, 3), c(2, 4)]
```

Extract the 3rd column from the tibble below.

```{r tibble-extract, exercise = TRUE}
df <- tibble(
  a = 1:4,
  b = 5:8,
  c = c("a", "b", "c", "d"),
  d = c(TRUE, FALSE, TRUE, FALSE)
)

```

```{r tibble-extract-check}
df <- tibble(
  a = 1:4,
  b = 5:8,
  c = c("a", "b", "c", "d"),
  d = c(TRUE, FALSE, TRUE, FALSE)
)

grade_result(
  pass_if(~ identical(.result, df[[3]]))
)
```

```{r tibble-extract-solution}
df <- tibble(
  a = 1:4,
  b = 5:8,
  c = c("a", "b", "c", "d"),
  d = c(TRUE, FALSE, TRUE, FALSE)
)

df[[3]]

# or

df[["c"]]
```





