## Assessment

1. On a scale of 1 to 10, with 1 being not competent and 10 being very competent, how competent do you think you are using the R programming language?

2. On a scale of 1 to 10, with 1 being very unlikely and 10 being very likely, how likely do they think it is that you will master the R language eventually

3. On a scale of 1 to 10, with 1 being very unejoyable and 10 being very enjoyable, how much do you enjoy learning R?

#### The following questions walk you through a short data analysis in R. Complete as many components as you can, feel free to skip any portions that you are unsure of.

You have a .csv file called `txhousing.csv`. Fill in the blank in the code below to read this into R.

```{r, eval = FALSE}
txhousing <- ________(file = "txhousing.csv")
```


```{r ex1-2, echo = FALSE}
question(
  '',
  answer("read_csv", correct = TRUE),
  answer("read.csv", correct = TRUE),
  type = c("always_correct", "learnr_text"),
  correct = "Answer Submitted."
)
```


Below is a data frame with information about the housing market in Texas.

```{r}
txhousing
```

```{r ex2-2, exercise = TRUE}
txhousing
```

```{r ex2_question1-2, echo = FALSE}
question(
  "How many observations are in this data frame? (You can use the console above to examine the dataset)",
  answer("0", correct = TRUE),
  answer("1000000", correct = TRUE),
  type = c("always_correct", "numeric"),
  correct = "Answer Submitted."
)
```

```{r ex2_question2-2, echo = FALSE}
question(
  "How many variables are in this data frame? (You can use the console above to examine the dataset)",
  answer("0", correct = TRUE),
  answer("1000000", correct = TRUE),
  type = c("always_correct", "numeric"),
  correct = "Answer Submitted."
)
```

Use the console below to filter the `txhousing` data frame to only include sales from years after `2013`.

```{r ex3-2, exercise = TRUE}

```

Use the console below to calculate the average number of sales by city.

```{r ex4-2, exercise = TRUE}

```

Create a new data frame called `txhousing_summary` with two columns: `city` and `average_sales` that contains the average number of sales by city. This data frame should have one row per city.

```{r ex5-2, exercise = TRUE}

```


```{r ex6-2, echo = FALSE}
question(
  "What is the average number of sales in Austin?",
  answer("0", correct = TRUE),
  answer("10000", correct = TRUE),
  type = c("always_correct", "numeric"),
  correct = "Answer Submitted."
)
```

