## Assessment

```{r, echo = FALSE}

shiny::sliderInput(inputId = "r-competence-3",
                   label = "On a scale of 1 to 10, with 1 being not competent and 10 being very competent, how competent do you think you are using the R programming language?", 
                   min = 1, 
                   max = 10, 
                   value = 5, 
                   step = 1)

shiny::sliderInput(inputId = "r-master-eventually-3",
                   label = "On a scale of 1 to 10, with 1 being very unlikely and 10 being very likely, how likely do they think it is that you will master the R language eventually?", 
                   min = 1, 
                   max = 10, 
                   value = 5, 
                   step = 1)

shiny::sliderInput(inputId = "r-enjoy-learning-3",
                   label = "On a scale of 1 to 10, with 1 being very unejoyable and 10 being very enjoyable, how much do you enjoy learning R?", 
                   min = 1, 
                   max = 10, 
                   value = 5, 
                   step = 1)

```

#### The following questions walk you through a short data analysis in R. Complete as many components as you can, feel free to skip any portions that you are unsure of.

You have a .csv file called `txhousing.csv`.

```{r, eval = FALSE}
txhousing <- ________(file = "txhousing.csv")
```

```{r ex1-3, echo = FALSE}
shiny::textInput("ex1-3", 
                 label = "In the text box provided, fill in the blank in the code above to read this into R.")
```

Below is a data frame with information about the housing market in Texas.

```{r}
txhousing
```

```{r ex2-3, exercise = TRUE}
txhousing
```

```{r ex2_question1-3, echo = FALSE}
shiny::numericInput("ex2-3",
                    "How many observations are in this data frame? (You can use the console above to examine the dataset)",
                    min = 0,
                    max = 100000000,
                    value = 0)
```

```{r ex2_question2-3, echo = FALSE}
shiny::numericInput("ex3-3",
                    "How many variables are in this data frame? (You can use the console above to examine the dataset)",
                    min = 0,
                    max = 100000000,
                    value = 0)
```

Use the console below to filter the `txhousing` data frame to only include sales from years after `2013`.

```{r ex3-3, exercise = TRUE}

```

Use the console below to calculate the average number of sales by city.

```{r ex4-3, exercise = TRUE}

```

Create a new data frame called `txhousing_summary` with two columns: `city` and `average_sales` that contains the average number of sales by city. This data frame should have one row per city.

```{r ex5-3, exercise = TRUE}

```

```{r ex6-3, echo = FALSE}
shiny::numericInput("ex4-3",
                    "What is the average number of sales in Austin?",
                    min = 0,
                    max = 100000000,
                    value = 0)
```
