## Lists and Data Frames


### Lists

An `R` _list_ is data structure consisting of an ordered collection of _components_. The components can be of different modes and types, for example, a list could be a collection of different types of vectors of different lengths, as seen below.

```{r}
list(numeric = c(1, 2, 3), 
     logical = TRUE,
     character = c("apple", "banana"))
```

Components of the list are _numbered_ and can be referenced using a double bracket. For example, you can reference the first element of a list with `[[1]]` as seen below.

```{r}
lst <- list(numeric = c(1, 2, 3), 
     logical = TRUE,
     character = c("apple", "banana"))
lst[[1]]
```

Components can also be referenced via their _names_. For example, the first element of the list below could be referenced by `[["numeric"]]`

```{r}
lst[["numeric"]]
```

#### Exercise

Combine the following four vectors into a list.

```{r list, exercise = TRUE}
x <- c(5, 1, 3)
y <- 1
z <- c("chickens", "roosters")
```

```{r list-check}
x <- c(5, 1, 3)
y <- 1
z <- c("chickens", "roosters")
grade_result(
  pass_if(~ identical(.result, list(x, y, z)))
)
```

### Data frames

A _data frame_ is a specific type of _list_ with the class `data.frame` or `tibble`. A `tibble` is a specific subclass of `data.frame` that has a few additional restrictions. Broadly, data frames consist of _rows_ and _columns_, where the length of the _rows_ is consistent for all _columns_. For example, here is a data frame with two columns, `x` and `y`, each with three rows.

```{r}
data.frame(
  x = c(1, 2, 3),
  y = c(4, 5, 6)
)
```

#### Exercise

Create a data frame using the `data.frame()` function consisting of two variables, `x` and `y`, detailed below.

```{r dataframe, exercise = TRUE}
x <- c(1, 2, 3)
y <- c("do", "re", "mi")
```

```{r dataframe-check}
x <- c(1, 2, 3)
y <- c("do", "re", "mi")
grade_result(
  pass_if(~ identical(.result, data.frame(x = x, y = y)))
)
```



