---
title: "Demographic Question Code"
author: "Jonathan Trattner"
date: "9/11/2020"
output: 
  html_document:
    fig.width: 7
    fig.asp: 0.718
    df_print: paged
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
      smooth_scroll: true
    theme: journal
    highlight: monochrome
    code_folding: hide
runtime: shiny
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(tidyr)
library(tibble)
library(shinyWidgets)
library(fs)
library(purrr)
library(pander)
library(rlang)


# I created a local directory
outputDir <- "storeDemographics"

# function based on Dean Attali's post about persistent data storage
# https://shiny.rstudio.com/articles/persistent-data-storage.html
saveData <- function(data, userID) {
  
  # Create a unique file name
  fileName <- base::sprintf("%s_%s.csv", userID, base::as.integer(base::Sys.time()))
  
  # Write the file to the local system
  readr::write_csv(data,
                   path = base::file.path(outputDir, fileName))
}



```

I think the question demographics should have the following structure. Four columns: 

1. `question`: The demographic question to ask. 
2. `option`: For questions that have options (like multiple choice or select questions), those values would go in thsi column. If the answers are not discrete variables, then there would be an NA which would get changed into "placeholder." 
3. `input_type`: This describes the input type. For example, "numeric" would create a `numericInput`, "select" would create a `pickerInput` (from shinyWidgets package), etc.
4. `label`: This becomes the column name when the data is saved. It also serves as the `id` for Shiny inputs (as in `input$`.

```{r read data, eval = TRUE, message = FALSE, warning = FALSE}

# read in local file
sample <- readr::read_csv('sampleDemographics.csv')
pander(head(sample))

# nest the sample data
# replace any NA with "placeholder"
nestedSample <- sample %>% 
  mutate(option = replace_na(option, "placeholder")) %>%
  group_by(question) %>%
  nest() %>%
  ungroup()

# slice the second question about first language
age <-nestedSample %>% 
  slice(1) %>% 
  unnest(data)

#default value is 25
Q1 <- rlang::expr(
      numericInputIcon(
          inputId = eval(unique(age$label)),
          label = eval(unique(age$question)),
          value = 25,
          icon = list(
            eval(unique(age$label))
            )
      )
  )


# slice the second question about first language
firstLang <-nestedSample %>% 
  slice(2) %>% 
  unnest(data)

# create a select input UI element based on firstLang
# pickerInput is from the shinyWidgets package. I'm not
# sure if we will need to specify the namespace
# inside of our final package. When I did so inside
# of rlang::expr, however, this didn't work.
Q2 <- rlang::expr(
    pickerInput(
      inputId = eval(unique(firstLang$label)),
      label = eval(unique(firstLang$question)),
      choices = firstLang$option,
      options = list(
      title = "Placeholder")
      )
    )


```

```{r make functional, eval = FALSE}


### First draft to automate this process.

getUICode <- function(df) {

  inputType <- unique(df$input_type)

  if (inputType ==  "select") {
  output <- rlang::expr(
    pickerInput(
      inputId = eval(unique(df$label)),
      label = eval(unique(df$label)),
      choices = df$option,
      options = list(
      title = "Placeholder")
      )
    )
  } else if (inputType == "numeric") {
    
    output <- rlang::enexpr(
      numericInputIcon(
          inputId = eval(unique(df$label)),
          label = eval(unique(df$label)),
          value = default,
          icon = list(
            eval(unique(df$label))
            )
      )
    )
  }
  return(output)
}

x <- getUICode(firstLang)


#' Create different input UIs based on questions.
#'
#' @param df 
#'
#' 
#' @importFrom rlang .data
#' @return
#' @export
#'

getInput <- function(df) {
  
  nested <- df %>% 
  dplyr::mutate(option = tidyr::replace_na(.data$option, "placeholder")) %>%
  dplyr::group_by(.data$question) %>%
  tidyr::nest() %>%
  dplyr::ungroup()
  
}


# Ignore for now:
# 
# loadData <- function() {
#   # Read all the files into a list
#   files <- fs::dir_ls(outputDir)
#   purrr::map_df(files, read_csv(.x)) 
# }

# walk(demList, ~eval(.x))


```

```{r, echo=FALSE}

shinyApp(

  ui = fluidPage(
    textInput("userID", "Enter your username."),
    eval(Q1),
    eval(Q2),
    actionBttn("submit", "Submit"),
    
  ),

  server = function(input, output, session) {
    
    #access session client data -- url port. I'm not sure if this is unique for each visitor with shinyapps.io. I'm including userID just for reference now.
    user_id <- reactive({paste0(input$userID, session$clientData$url_port)})
    
    # The input$first_language is hard coded. I'm not sure how to change that.
    # It should be something like `eval(unique(firstLang$label))`
    formData <- reactive({
      data <- tibble::tribble(~userID, ~language,
                      input$userID, input$first_language)
      data
    })
    
    observeEvent(input$submit, {saveData(data = formData(), userID = user_id())})
    
    },

  options = list(height = 500)
)


```
